---
title: Disk Benchmarks - qsave
output: html_document
---

## Simulate the user's environment

Data set creation function

```{r make_df}
make_df <- function(nrow, ncol) {
  cbind(
    as.data.frame(matrix(
      runif(nrow * ncol), nrow = nrow, ncol = ncol
    )),
    rep(
      'THIS IS A VERY LONG TEXT STRING TO TEST A THEORY ABOUT THE STRING CACHE THIS IS A VERY LONG TEXT STRING TO TEST A THEORY ABOUT THE STRING CACHE',
      nrow
    ),
    rep(
      'THIS IS A DIFFERENT VERY LONG TEXT STRING TO TEST A THEORY ABOUT THE STRING CACHE THIS IS A VERY LONG TEXT STRING TO TEST A THEORY ABOUT THE STRING CACHE',
      nrow
    )
    
  )
  
}
```


Figure out how much data to create

```{r calc_rows}
# This will give us a data set of about 103G when saved
rows_needed <- round(500 * 1024 * 1024 / (8001904 / 100000) * 2.5)
```

Create the data

```{r create_data}
local({
  df <- make_df(nrow = rows_needed, ncol = 3)
  
  for (i in 1:20) {
    assign(paste0("df", i), df, envir = parent.env(environment()))
  }
})
```

How big is each dataframe in memory?

```{r df_size}
object.size(df1) / 1e6
lobstr::obj_size(df1) / 1e6
ls()
```


## Session save with the qs package

qs uses a facebook designed compression algorithm and a multi-threaded design.

Here we parallelise across half the available cores.

### EFS

```{r efs_write}
ls()
library(qs)
filename <- "/home/efs-mount/mark/session_efs.qs"
if (file.exists(filename)){
  unlink(filename)
}
Sys.time()
system.time(
  do.call(qs::qsavem, c(lapply(ls(), as.symbol), file = filename, nthreads = parallel::detectCores()/2))
)
Sys.time()
round(file.size(filename)/(1024*1024*1024), 1) # to get bytes to GBytes
```

### EBS

```{r ebs_write}
filename <- "/ebs-local/session_ebs.qs"
if (file.exists(filename)){
  unlink(filename)
}
Sys.time()
system.time(
  do.call(qs::qsavem, c(lapply(ls(), as.symbol), file = filename, nthreads = parallel::detectCores()/2))
)
Sys.time()
round(file.size(filename)/(1024*1024*1024), 1) # to get bytes to GBytes
```

## Session restore with qs

### EFS

```{r efs_restore}
rm(list = ls())
filename <- "/home/efs-mount/mark/session_efs.qs"
Sys.time()
system.time(qload(filename, nthreads = parallel::detectCores()/2))
Sys.time()
```

Check that everything has loaded properly

```{r efs_clean}
lobstr::obj_size(df1) / 1e6
ls()
unlink(filename)
```

### EBS

```{r ebs_restore}
rm(list = ls())
filename <- "/ebs-local/session_ebs.qs"
Sys.time()
system.time(qload(filename, nthreads = parallel::detectCores()/2))
Sys.time()
```

Check that everything has loaded properly

```{r ebs_clean}
lobstr::obj_size(df1) / 1e6
ls()
unlink(filename)
```


EFS. Benchmarking functions

```{r efs_write}
library(qs)
filename <- "/home/efs-mount/mark/session_efs.qs"
qs_session_save <- function(filename){
  
  if (file.exists(filename)){
    unlink(filename)
  }
  do.call(qs::qsavem, c(lapply(ls(), as.symbol), file = filename, nthreads = parallel::detectCores()/2))
}


qs_session_restore <- function(filename){
  qload(filename, nthreads = parallel::detectCores()/2)
}
```

## Test save

```{r qs_session_save}
bench::mark(qs_session_save("/home/efs-mount/mark/session_efs.qs"), iterations = 10)
bench::mark(qs_session_save("/ebs-local/session_ebs.qs"), iterations = 10)
```

```{r qs_session_save_time}
system.time(qs_session_save("/home/efs-mount/mark/session_efs.qs"))
system.time(qs_session_save("/ebs-local/session_ebs.qs"))
```

## Test restore

```{r qs_session_save}
system.time(qs_session_restore("/home/efs-mount/mark/session_efs.qs"))
system.time(qs_session_restore("/ebs-local/session_ebs.qs"))
```

```{r qs_session_save}
bench::mark(qs_session_restore("/home/efs-mount/mark/session_efs.qs"), iterations = 10)
bench::mark(qs_session_restore("/ebs-local/session_ebs.qs"), iterations = 10)
```
